Concurrent Programming with CXL

### 2020-06-15 book/paper.tex
Latest

@@

\begin{itemize}
\item \texttt{False < True};
\item integers are ordered in the natural way;
\item atoms are lexicographically ordered;
\item program counters are ordered by their integer values;
\item dictionaries are first converted into a list of ordered (key, value)
pairs.  Then two dictionaries are lexicographically ordered by this
representation;
\item a set is first converted into an ordered list, then lexicographically
ordered;
\item an address is a list of atoms.  Addresses are lexicographically
ordered accordingly;
\item contexts (Appendix~\ref{app:context} are ordered by hash.
\end{itemize}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{figures/barrier.jpeg}
\end{center}
\caption{High-level state diagram specification of barrier synchronization
with three processes and three rounds.  The three numbers specify the round
number of each process.}
\label{fig:barrierdiagram}
\end{figure}

@@

\begin{itemize}
\item \texttt{False < True};
\item integers are ordered in the natural way;
\item atoms are lexicographically ordered;
\item program counters are ordered by their integer values;
\item dictionaries are first converted into a list of ordered (key, value)
pairs.  Then two dictionaries are lexicographically ordered by this
representation;
\item a set is first converted into an ordered list, then lexicographically
ordered;
\item an address is a list of atoms.  Addresses are lexicographically
ordered accordingly;
\item contexts (Appendix~\ref{app:context}) are ordered by hash.
\end{itemize}
